% ---------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
% ---------------------------------------------

\documentclass[11pt]{scrartcl}

% Move the margin to the left of the page
\reversemarginpar

% New command defining the margin text style
\newcommand{\MarginText}[1]{\marginpar{\raggedleft\itshape\small#1}} 

% Use the classicthesis style for the style of the document
\usepackage[nochapters, pdfspacing]{classicthesis} 

% Use the currvita style for the layout of the document
\usepackage[TextAligned, NoDate]{currvita} 

% Font color of your name at the top
\renewcommand{\cvheadingfont}{\LARGE\color{Green}}

% Required for adding links	and customizing them
\usepackage{hyperref} 

% Set link colors
\hypersetup{colorlinks, breaklinks, urlcolor=Blue, linkcolor=Blue}

 % Set the width of the date box in each block
\newlength{\datebox}\settowidth{\datebox}{Spring 2011}

% Define a command for each new block - change spacing and font sizes here: #1 is the left margin, #2 is the italic date field and #3 is the position/employer/location field
\newcommand{\NewEntry}[3]{\noindent\hangindent=0.25em\hangafter=0 \parbox{\datebox}{\small \textit{#1}}\hspace{1.5em} #2 #3

% Add some white space after each new entry
\vspace{0.5em}}

% Define a command for descriptions of each entry - change spacing and font sizes here
\newcommand{\Description}[1]{\hangindent=0.25em\hangafter=0\noindent\raggedright\footnotesize{#1}\par\normalsize\vspace{1em}} 

% ----------------------------
\begin{document}
\thispagestyle{empty} % Stop the page count at the bottom of the first page
% ----------------------------

% ---------------------
% PERSONAL INFORMATION
% ---------------------

% Your name
\begin{cv}{\spacedallcaps{Ronnie Joshua}}\vspace{0.5em}

% Personal information heading
\noindent\spacedlowsmallcaps{Personal Information}\vspace{1em} 

% Phone number(s)
\NewEntry{phone}{(M) +972 (58) 517 1183} 

% Email address
\NewEntry{email}{\href{mailto:ron.juden@gmail.com}{ron.juden@gmail.com}} 

% Linkedin Profile
\NewEntry{linkedin}{\href{https://www.linkedin.com/in/ronnie-joshua/}{https://www.linkedin.com/in/ronnie-joshua/}} 

 % Personal website
\NewEntry{website}{\href{http://www.webanalyticsinfo.com}{http://www.webanalyticsinfo.com}}

% Github Profile
\NewEntry{github}{\href{https://github.com/ronniejoshua}{https://github.com/ronniejoshua}} 

% Extra white space between the personal information section and goal
\vspace{0.5em} 

% Goal heading, could be used for a quotation or short profile instead
\noindent\spacedlowsmallcaps{My Area of Interest \& Vision}\vspace{0.5em} 

% Goal text
\Description{\textbf{\uppercase{Vision:}} Designing, Developing \& Implementing Tools \& Techniques for Data-Driven Decision-Making. \textbf{\uppercase{Area of Interest:}} Business Intelligence Development, Digital Marketing Analytics \& Optimization, Data Development \& Data Engineering.}\vspace{0.5em} 

% -----------------
% WORK EXPERIENCES
% ----------------

\noindent\spacedlowsmallcaps{Work Experience}\vspace{1em}

\MarginText{\textbf{abaGada Internet Ltd.}}

\NewEntry{\textbf{2019/06 - }}{\textbf{Business Intelligence \& Analytics Developer}, \textsc{IL}}

\Description{AbaGada is a leading Performance Marketing agency and part of the global Dentsu Aegis Network. abaGada manages high scale global multi-dimensional marketing activities for high profile, big brands. Major Clientele: \textbf{Google \& Waze}}

\Description{\textbf{\uppercase{Achievements: }}\newline End to end development of extensive \& robust data pipelines in python 3 including designing, development, testing, deploying \& providing maintenance \& support. Create new and optimize existing ETL \& ELT processes. Work closely with the tech lead on design and implementation of big data solutions. \newline\newline Developed Data Connectors from various Advertising Platform to Big Query in Python. \textbf{Platforms Include:} Facebook, Google Ads, Linkedin, Twitter, Outbrain, Snapchat, Microsoft Ads, Liftoff, Display \& Video 360 and Taboola.
}

\Description{\textbf{Technology Stack:} Google Cloud Platform(GCP) -- Extensively worked on Big Query, Cloud Storage, Compute Engine, App Engine, Cloud Functions, Cloud Scheduler, Cloud Source Repositories, Dataflow. Leveraging Apache Beam \& Apache Airflow for creating and maintaining data pipelines. Comfortable working in a Linux based environment.}

\Description{\textbf{Scripting Languages:} Python, Javascript, SQL, Google Apps Script(Google Sheets) \& Shell Scripting}
% ------------------------------------------------


% Extra space between major sections
\vspace{0.25em}
\MarginText{Previous Experiences \& Certifications}

\Description{{\href{https://www.linkedin.com/in/ronnie-joshua/}{\textbf{Please click here to visit my Linked-in profile for more information on my previous employment experiences and certifications}}}}

% -----------------
% COMPUTER SKILLS
% ----------------
\noindent\spacedlowsmallcaps{Technology Stack}\vspace{0.50em}

\Description{\MarginText{Advanced}\textsc{python}, \textsc{sql}}

\Description{\MarginText{Intermediate}\textsc{Javascript}, \textsc{Google Analytics}, \textsc{Google Tag Manager}}

\Description{\MarginText{Basic}\textsc{R Programming}, \textsc{Shell Scripting}, \textsc{html5}, \textsc{css}, \textsc{git vcs}, \textsc{docker} }

% ----------

% ------------------------
% Academic Qualifications
% -----------------------
\spacedlowsmallcaps{Academic Qualifications}\vspace{1em}

\MarginText{\textbf{Masters of Arts}}

\NewEntry{2004-2006}{Department of Economics, Gujarat University, India}

\Description{\textit{\textbf{First Class Honours}}\ \ $\cdotp$\ \ School: University School of Social Sciences. 
\newline \textbf{Major: Economic \& Financial Theory}
\newline \textbf{Minor: Mathematical Economics, Statistics \& Econometric Methods}}
% -------------
\end{cv}
\end{document}
% -------------
